chapter_4_ka
============

```{r}
library(ISLR)
library(class)
```

Question #10
```{r}
names(Weekly)
summary(Weekly)
pairs(Weekly)
plot(Weekly$Year, Weekly$Volume)
cor(Weekly[,-9])
```

```{r}
summary(glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Weekly, family=binomial))
glm.fit = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Weekly, family=binomial)
glm.probs = predict(glm.fit, type="response")
glm.pred = rep("Down", dim(Weekly)[1])
contrasts(Weekly$Direction)
glm.pred[glm.probs > 0.5] = "Up"
table(glm.pred, Weekly$Direction)
mean(glm.pred == Weekly$Direction)

http://stackoverflow.com/questions/11838278/plot-with-conditional-colors-based-on-values-in-r?rq=1
```{r}
plot(Weekly$Volume, Weekly$Lag2, col=ifelse(Weekly$Direction == 'Up', 'blue', 'red'), pch=19)
```

Now considering train data from the period: 1990 to 2008
And consider the predictor which has been significant.
```{r}
train = (Weekly$Year <= 2008)
```

Logistic Regression
```{r}
train.model.LR = glm(Direction~Lag2, data=Weekly, family=binomial, subset=train)
LR.probs = predict(train.model.LR, newdata = Weekly[!train,], type="response")
LR.pred = rep("Down", length(LR.probs))
LR.pred[LR.probs > 0.5] = "Up"
table(LR.pred, Weekly[!train,]$Direction)
mean(LR.pred == Weekly[!train,]$Direction)
```

Linear Discriminant Analysis
```{r}
train.model.LDA = lda(Direction~Lag2, data=Weekly, subset=train)
summary(train.model.LDA)
LDA.pred = predict(train.model.LDA, newdata=Weekly[!train,])
names(LDA.pred)
LDA.class = LDA.pred$class
table(LDA.class, Weekly[!train,]$Direction)
mean(LDA.class == Weekly[!train,]$Direction)
```

Quadratic Discriminant Analysis
```{r}
train.model.QDA = qda(Direction~Lag2, data=Weekly, subset=train)
QDA.pred = predict(train.model.QDA, newdata=Weekly[!train,])
names(QDA.pred)
QDA.class = QDA.pred$class
table(QDA.class, Weekly[!train,]$Direction)
mean(QDA.class == Weekly[!train,]$Direction)
```

K-Nearest Neighbor
http://stackoverflow.com/questions/19396947/how-can-i-resolve-the-following-dimension-mismatch-with-rs-k-nearest-neighbors
```{r}
train.X = Weekly[train,]$Lag2
test.X = Weekly[!train,]$Lag2
knn.pred = knn(data.frame(train.X), data.frame(test.X), train.Direction, k=1)
table(knn.pred, Weekly[!train,]$Direction)
mean(knn.pred == Weekly[!train,]$Direction)
```